CTest Integration of Sikuli Automated GUI Testing

### 2011-06-17 Documentation/Article.tex
Completed draft of Intro.  Also included questions in comments.

>>>>

%Should this be in the abstract instead?
% difference between Abstract and Introduction?

GUI testing is a key aspect of software development. Having a well defined testing protocol is very
important in maintaining a productive flow, especially on the eve of a new release.  As the software becomes 
more complex, testing each feature can be immensely time consuming.  
We collected a list of over 400 different GUI tests which
involved endlessly repetitive clicking and checking.  This task took around 5 hours to complete each time a new release was ready.
And debugging would push release dates back days or even weeks.  We decided to tackle this problem by utilizing a new
scripting language called Sikuli that can automate any visual operation.  In this way we could write scripts to automate the GUI testing.
This cut the time to complete each test drastically.  Furthermore, we have integrated the automated tests with CTest.  Therefore we will be able to
run the collection of tests every night and find bugs as they arise instead of the night before a new release.  As a result,
the rate of new releases increased drastically.

% Should the intro be about GoFigure2? with picture of GoFigure2
% Also consult actual number of tests.
%See Figure 3 ? -- picture of GIT log from presentation
